On consistency scores in text data with an implementation in R

### 2021-01-08 outputs/documents/paper_ngrams.Rmd
minor update

The consistency score is calculated by the number of words that have been predicted by the model divided by the total number of words in the data. The function identifies the counts of words that are predicted by the model and divided by the total number of words in the internal consistency dataset:

@@

The next step is to compare the text to be evaluated with the internal consistency dataset that we created in the previous step. The function `aRianna::generate_internal_consistency_score()` takes two arguments — the text to evaluate and the internal consistency dataset. The function identifies the word 'na' as an unexpected word, and generates the internal consistency score as zero. The function also lists 'no' as the replacement of 'na':

@@

To get the external consistency score, we use the `aRianna::generate_external_consistency_score()` function. The function `aRianna::generate_internal_consistency_score()` takes in only one argument — the text to evaluate, and compares it with the external consistency dataset. Here, the text to evaluate is 'there was no possibiliti', with the word "possibility" being wrongly spelled. The function identifies the word 'possibiliti' as an unexpected word, and generates the external consistency score 0.333. Because the external dataset is larger, it is capable of providing more replacement candidates for 'possibiliti'. There are no replacements based on 5-grams, so the replacements based on 4-grams are displayed first, followed by the replacements based on tri-grams:

>>>>

The consistency score is calculated by the number of words that have been predicted by the model divided by the total number of words in the data. The function identifies the counts of words that are predicted by the model and divided by the total number of words in the input text:

@@

The next step is to compare the text to be evaluated with the internal consistency dataset that we created in the previous step. The function `aRianna::generate_internal_consistency_score()` takes two arguments — the text to evaluate and the internal consistency dataset. The function identifies the word 'na' as an unexpected word, and generates the internal consistency score as 0.8. The function also lists 'no' as the replacement of 'na':

@@

To get the external consistency score, we use the `aRianna::generate_external_consistency_score()` function. The function `aRianna::generate_internal_consistency_score()` takes in only one argument — the text to evaluate, and compares it with the external consistency dataset. Here, the text to evaluate is 'there was no possibiliti', with the word "possibility" being wrongly spelled. The function identifies the word 'possibiliti' as an unexpected word, and generates the external consistency score 0.75. Because the external dataset is larger, it is capable of providing more replacement candidates for 'possibiliti'. There are no replacements based on 5-grams, so the replacements based on 4-grams are displayed first, followed by the replacements based on tri-grams:
